---
title: "Exploration of 2019 CES data"
author: "Jiahui Pan"
date: "September 28, 2020"
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("tidyverse")
# install.packages("devtools")
#devtools::install_github("hodgettsp/cesR")
# install.packages("visdat")
# install.packages("skimr")
library(tidyverse)
library(devtools)
library(cesR)
library(visdat)
library(skimr)
library(ggplot2)
```

# abstract
We plotted a histogram on the ages in 2019 CES Online surveys and performed data diagnistics. The results showed young people are inactive to participate in the surveys.


# Introduction
CES data reflects Canadians' political behaviour and attitudes and provides an unparalleled snapshot and record of Canadian society and political life.
We investigated the 2019 CES data and performed data diagnoistics on the distribution ages,and results showed young people are inactive to participate in the surveys.
There may exists response erro.

```{r download, warning=FALSE, message=FALSE}
cesR::get_ces("ces2019_web")
```


```{r}
ces2019_web %>% ggplot(aes(cps19_age)) + geom_histogram(binwidth = 1) +
  labs(x = "age", 
       y = "number",
       title = "Distribution of age in 2019 CES Online surveys") +
  theme_bw()
```

## Graph discussion
In this graph we find the distribution of age is lightly skewed to the right.

# Discussion
We find the count of age 100 is too high,which is a response error.
Young people(under 30) are inactive to take the survey,which may cause inadequate frame-coverage error.

## Weakness
Sample size is small compared to the entire population.
Response error exists and it is hard to identified and eliminated.

# Reference
- Wickham et al., (2019). Welcome to the tidyverse. Journal of
  Open Source Software, 4(43), 1686,
- Stephenson, Laura B; Harell, Allison; Rubenson, Daniel; Loewen, Peter John, 2020, '2019 Canadian Election Study - Online Survey', 
- Stephenson, Laura, Allison Harrel, Daniel Rubenson and Peter Loewen. Forthcoming. 'Measuring Preferences and Behaviour in the 2019 Canadian Election Study,' Canadian Journal of Political Science.
- Hadley Wickham, Jim Hester and Winston Chang (2020).
  devtools: Tools to Make Developing R Packages Easier.
- Elin Waring, Michael Quinn, Amelia McNamara, Eduardo Arino
  de la Rubia, Hao Zhu and Shannon Ellis (2020). skimr:
  Compact and Flexible Summaries of Data.
- Tierney N (2017). “visdat: Visualising Whole Data Frames.”
_JOSS_, *2*(16), 355. doi: 10.21105/joss.00355